{\let\cleardoublepage\relax \chapter*{Management and Organization}}
\addcontentsline{toc}{chapter}{Management and Organization}

As an S Corporation, Cereus is required to have a board of directors \cite{UpCounsel.2020}. We are required to pay all employees a reasonable salary, have only one class of stock, have less than 100 shareholders, and all shareholders must be U.S. citizens or legal residents \cite{wave.2019}. Given that we do not anticipate hiring any employees during the first year of operations, the three founders will be required to manage all operations including support, sales, marketing, engineering, and product. 

\section{Professional and Advisory Support}

\subsection{Board of Directors}

Initially, all company stock will be held by the three founders. The board of directors will consist of five people -- including the three founders. The other two board members will be elected by the three founders identifying local leaders, preferably with experience in software development, marketing, privacy law, and/or data science. Should any board member be incapacitated or ask to be dismissed, the remaining board members will elect a replacement.

\subsection{Attorney}

As discussed in the \nameref{legal.environment} section, Cereus will consult with an attorney to establish terms of use and release of liability contract to be used for all of our customers. We don't anticipate the need for a permanent attorney position during our first year of operations. As the company grows, our products expand, and legislation is passed or changed; the need for a full-time attorney may be justified. 

\subsection{Accountant}

In the \nameref{section.admin.costs} section, we established that accounting and account management will be managed by a third-party, with a budget of \$200 per month. Should the company grow and require a larger budget, the board of directors will consider hiring a part-time accountant during the first year of operations.

In the event the board determines the need for a part-time accountant, the new employee will be in charge of managing all company financial documents. Responsibilities will include: ensuring the accuracy of our financial documents, general financial reporting, and managing customer accounts.

The preparation of tax returns will be managed by an external firm.

\subsection{Insurance Agent, Banker}

During the first year of operations, Cereus does not anticipate a significant volume of work in the insurance or banking departments. These areas of work will be contracted to third-parties.

\subsection{Mentors and Key Advisors}

Cereus's primary mentors and key advisors will be local business owners and community leaders. Ideally, these entrepreneurs will be a part of our board of directors during the first year.