{\let\cleardoublepage\relax \chapter*{Financial Plan}}
\addcontentsline{toc}{chapter}{Financial Plan}

\section{Assumptions}

Cereus's financial plan is based on the operational costs described in the \nameref{section.admin.costs} section. Forecasted sales for our first year can be found in Table \ref{table.sales.forecast} and start-up expenses in the \nameref{startup.exp} section. Supplier billing takes place every 30 days (\nameref{infra.costs}) and customers are billed the first of each month (\nameref{transaction.process}).

\subsection{Revenue Assumptions}

Total revenue, including costs associated with operating each tier, is projected to be \$11,013.36 during our first year of operations (Table \ref{table.sales.forecast}). This is under the assumption that our marketing campaigns have a 1\% conversion rate and that all assumptions in the \nameref{section.sales.forecast} section are met.

\subsection{Financing}

Cereus's three founders will make an initial investment of \$8,500.00 to cover a year's worth of known expenses, start-up costs, and contingencies.

\subsection{Startup Expenses}

Our startup budget, including a 10\% contingency budget, is estimated to be \$875.75 (\nameref{startup.exp}).

\subsection{Operational Expense Assumptions}

General infrastructure operations, for auditing up to 100 websites, is expected to be around \$157.14 per month (\nameref{infra.costs}). We will budget \$250 per month for advertising and promotion (\nameref{section.admin.costs}). Up to \$200 per month will be reserved for general accounting purposes (\nameref{section.admin.costs}).

We anticipate our operating expenses to be around \$607.14 per month.

\section{Profit and Loss Projection}

Cereus's yearly profit loss and projection for the first year is provided in Table \ref{table.profit.loss}. As an S Corporation, tax responsibilities fall to our shareholders (the founders) and are not reflected in the table (\nameref{legal.ownership}).

Using the forecasted sales of each subscription, the cost associated with each subscription, and estimated operation expenses, Table \ref{table.profit.loss} reveals that it make take up to six months before Cereus is profitable.

%\begin{sidewaystable}
\begin{table}[H]
  \caption{Monthly Profit and Loss Projection.}
  \setlength\tabcolsep{2pt}
  \def\arraystretch{1.2}%
  \scriptsize

  \begin{tabularx}{\textwidth}{X X X X X X X X X X X X X}

    \multicolumn{13}{c}{\textbf{Month}} \\

    \hline
    
    \multicolumn{1}{c}{} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10} & \textbf{11} & \textbf{12}  \\

    \hline

    \multicolumn{13}{l}{\textbf{Subscription Revenue}} \\

    \hline

    \multicolumn{1}{r}{Personal} & 78.00 & 156.00 & 156.00 & 156.00  & 156.00  & 156.00  & 156.00  & 156.00  & 195.00  & 273.00  & 390.00  & 468.00  \\
    \multicolumn{1}{r}{Professional} &   &   &  &   &  &  &  &  &  &  &  &  \\
    \multicolumn{1}{r}{Enterprise} &  &  &  &  &  & 1299.00 & 1299.00 & 1299.00 & 1299.00 & 1299.00 & 1299.00 & 1299.00  \\

    \multicolumn{1}{r}{Total} & 78.00 & 156.00 & 156.00 & 156.00  & 156.00  & 1455.00  & 1455.00  & 1455.00  & 1494.00  & 1572.00  & 1689.00  & 1767.00  \\

    \hline

    \multicolumn{13}{l}{\textbf{Costs of Goods Sold}} \\

    \hline

    \multicolumn{1}{r}{Free} & 0.60 & 1.10  & 1.90 & 2.70 & 3.30 & 3.90 & 4.70 & 5.50 & 6.20 & 6.80 & 7.30 & 7.80  \\
    \multicolumn{1}{r}{Personal} & 4.12 & 8.24 & 8.24 & 8.24 & 8.24 & 8.24 & 8.24 & 8.24 & 10.30  & 14.42 & 20.06 & 24.18  \\
    \multicolumn{1}{r}{Professional} &  &  &  &  &  &  &  &  &  &  &  &   \\
    \multicolumn{1}{r}{Enterprise} &  &  &  &  &  & 55.86 & 55.86 & 55.86 & 55.86 & 55.86 & 55.86 & 55.86  \\

    \multicolumn{1}{r}{Total} & 4.72 & 9.34 & 10.14 & 10.94 & 11.54 & 68.00 & 68.80 & 69.60 & 72.36 & 77.08 & 83.22 & 87.84  \\

    \hline

    \multicolumn{1}{l}{Expenses} & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14 & 607.14  \\

    \multicolumn{1}{l}{Net} & -533.86 & -460.48 & -461.28 & -462.08 & -462.68 & 779.86 & 779.06 & 778.26 & 814.50 & 887.78 & 998.64 & 1072.02  \\

  \end{tabularx}
  \label{table.profit.loss}
\end{table}
%\end{sidewaystable}


\section{Cash-Flow Projection}

Cereus is projected to be profitable within 12 months of operations. The first 6 months of operations depict the company being cash-positive, though not profitable (Table \ref{table.sales.forecast}). The cash balance is estimated to be \$11,354.00 by the end of the year (Table \ref{table.cash.flow}). 

\begin{sidewaystable}
\begin{table}[H]
  \caption{Monthly cash flow.}

  \begin{tabularx}{\textwidth}{X X X X X X X X X X X X X}

    \multicolumn{13}{c}{\textbf{Month}} \\

    \hline
    
    \multicolumn{1}{c}{} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10} & \textbf{11} & \textbf{12}  \\

    \hline

    \multicolumn{13}{l}{\textbf{Ingress}} \\

    \hline

    \multicolumn{1}{r}{Subscriptions} & 78.00 & 156.00 & 156.00 & 156.00  & 156.00  & 1455.00  & 1455.00  & 1455.00  & 1494.00  & 1572.00  & 1689.00  & 1767.00  \\
    \multicolumn{1}{r}{Financing} & 8500.00 &  &  &  &  & &  &  &  &  &  &  \\

    \hline

    \multicolumn{13}{l}{\textbf{Egress}} \\

    \hline

    \multicolumn{1}{r}{Operations} & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14 & 157.14  \\
    \multicolumn{1}{r}{Marketing} & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00 & 250.00  \\
    \multicolumn{1}{r}{Accounting} & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00 & 200.00  \\
    \multicolumn{1}{r}{Infrastructure} & 4.72 & 9.34 & 10.14 & 10.94 & 11.54 & 68.00 & 68.80 & 69.60 & 72.36 & 77.08 & 83.22 & 87.84  \\
    \multicolumn{1}{r}{Startup} & 875.75 &  &  &  &  &  &  &  &  &  &  &   \\

    \hline

    \multicolumn{13}{l}{\textbf{Totals}} \\

    \multicolumn{1}{l}{Total Cash Flow} & 7090.39 & -460.48 & -461.28 & -462.08 & -462.68 & 779.86 & 779.06 & 778.26 & 814.50 & 887.78 & 998.64 & 1072.02  \\
    \multicolumn{1}{l}{Beginning Cash} & 0.00 & 7090.39 & 6629.91 & 6168.63 & 5706.55 & 5243.87 & 6023.73 & 6802.79 & 7581.05 & 8395.55 & 9283.33 & 10281.98  \\
    \multicolumn{1}{l}{Ending Cash} & 7090.39 & 6629.91 & 6168.63 & 5706.55 & 5243.87 & 6023.73 & 6802.79 & 7581.05 & 8395.55 & 9283.33 & 10281.98 & 11354.00  \\

  \end{tabularx}
  \label{table.cash.flow}
\end{table}
\end{sidewaystable}

\section{Opening Day Balance Sheet}

Cereus will not have any inventory, pre-paid expenses, equipment, liabilities, or real estate. Assets on opening day will be equal to the investor's initiate contribution with start-up, accounting, and marketing expenses deducted. On opening day, Cereus will have \$7,174.25 in assets -- solely cash.

\section{Break-Even Analysis}

Table \ref{table.cereus.breakeven} calculates the number of subscriptions from each tier, including the cost to run each subscription, to break even with an infrastructure to support the auditing of up to 100 websites. This can be any mix of our subscription tiers, but at minimum, we will require any of the following: 17 personal subscriptions, 7 personal subscriptions, or 1 enterprise subscription.
