{\let\cleardoublepage\relax \chapter*{Conclusion}}
\addcontentsline{toc}{chapter}{Conclusion}

The purpose of this research was to determine the feasibility of founding a privacy company that provides automated auditing services. Over the past ten years, I’ve implemented dozens of consent management platforms for hundreds of websites. After conducting several audits, I began to notice that many of my practices could be automated. Initially, I developed general tools to assist me with day-to-day operations. As time progressed, these tools became the products discussed in this business plan.

The proposed company, Cereus, is a software-as-a-service company offering privacy compliance auditing tools and solutions for businesses that collect customer information through their websites. We will ensure that a website, and any new features, meet the compliance standards customers have defined within our systems before deployments reach their users. This enables companies to communicate with their partners in an efficient, compliant way – allowing our customers to focus on developing their products for their audience.

Sales forecasts for each month were simulated for the first year. Assumptions, as discussed in the \nameref{section.sales.forecast} Section, were made to estimate the conversion rate for our digital marketing campaigns. A percentage of the conversion rate, based on our open beta subscriptions, was applied to determine how many customers would subscribe to each tier. The simulation identified that Cereus has the potential to be profitable after 6 months of operations (Table \ref{table.profit.loss}).

The next steps involve the establishment of the board of directors, registration of the company, formulation of our marketing campaign, and the launch of our website. Customer feedback from our beta phase will be reviewed to determine which features will be required for our official release, and which will be included in future releases. An accounting agency will also have to be hired.

Lastly, this business plan is a living document. As the company grows, markets fluctuate, and the industry changes; the business plan will adapt. We will, initially, offer automated privacy auditing tools for our customers. Should our auditing tools prove to be successful in the privacy software market, we will aim to expand our services to be a consent management provider.