{\let\cleardoublepage\relax \chapter*{Executive Summary}}
\addcontentsline{toc}{chapter}{Executive Summary}

Consent management platform (CMP) vendors provide services that enable companies to inform their users about the types of information their website will collect and how it will be used. The consent management process will be automated by the vendor and make it easier for companies to meet the standards set by data and privacy compliance regulations \cite{cmp.what.2020}. The process of ensuring a website's integration with a CMP results in being compliant with regulations, however, is often manual and subject to human error.

At Cereus, we aim to become the leader in cutting-edge privacy compliance auditing tools by allowing our customers to request audits on-demand, or by linking our services into any continuous integration system. This ensures that a website, and any new features, meet the compliance standards customers have defined within our systems before deployments reach their users. Should an audit fail to meet compliance standards, stakeholders will be notified via email with an audit summary.

The auditor incorporates our belief that compliance involves more than the concept of "cookie consent." Our audits augment cookie consent by providing insights into the requests made on the website. This involves the requested resource, response status code, the type, size of the information exchanged, stack/callee trace, and whether or not the request met compliance expectations. With this information, our customers will be able to quickly identify where the compliance infringement originated and respond accordingly.

We serve the privacy management software market, which is expected to grow from an estimated US \$808.8 million (2019) to a total of \$6.1 billion by 2026 \cite{qy.2020}. We offer flexible subscriptions for any sized organization that's looking for privacy compliance auditing. It may, however, be difficult to market smaller companies that our services are worth mitigating the risk of being fined. Our primary focus is medium to large-sized organizations managing multiple websites. 

Our niche within the privacy management software market emphasizes privacy compliance auditing. In our \nameref{competitive.analysis}, we identified some industry leaders in the privacy management software and auditing markets. We speculate that our automated services will reduce the need for manual privacy compliance audits, but not necessarily replace them. The primary competition will come from privacy management software vendors with the technical capabilities to implement similar auditing utilities in addition to their CMP. Our greatest advantage against mature privacy software vendors will be our artificial intelligence capabilities and time present in the privacy auditing market.

Under the assumption of an initial investment of \$8,500.00 from the founders to begin operations, a marketing budget of \$250.00 per month for advertisements, and a 1\% conversion rate; our operations have the potential to be profitable within 6 months without any external funding. Less than favorable marketing conditions will delay our company's break-even date an additional 6 months. Even with unfavorable marketing conditions, our company will have a positive cash balance with no liabilities.

%Some assumptions were made when forecasting sales and profitability of our company. An initial investment of \$8,500.00 from the founders would be made to begin operations. We estimated that with a marketing budget of \$250.00 per month for advertisements and a 1\% conversion rate, our operations have the potential to be profitable within 6 months without any external funding. Less than favorable marketing conditions reveal our company breaking even after 12 months. In both scenarios, the company had a positive cash balance and no liabilities.

%%%%



